基于卷积神经网络的视频目标跟踪算法研究

### 2021-02-02 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
新增一些图
新增图像

\iffalse
\begin{figure}[t]
    \includegraphics{images/Arch7.pdf}
    \caption{我们基于全球时空感知（GSTP）的跟踪系统的架构。}
    \label{fig:arch}
\end{figure}
\fi

@@

\iffalse
\begin{figure*}
    \centering
    \includegraphics[width=17cm]{images/SiamRCNN.pdf}
    \caption{Architecture of SiamRCNN.}
    \label{fig:siamrcnn}
\end{figure*}
\fi

@@

\section{实验}
\label{sec:experiments}
\iffalse
\begin{figure}[htb]
    \includegraphics[width=8.6cm]{images/success_plot.png}
    \caption{Overall performance on GOT-10k, ranked by their average overlap (AO) scores.
}
    \label{fig:ao}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[t]
\begin{center}
\subfigure[]{
	\includegraphics[width=0.47\linewidth]
	{images/UAV20L/quality_plot_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.47\linewidth]
	{images/UAV20L/quality_plot_error_OPE_threshold.png}
}
\end{center}
   \caption{Success and precision plots on UAV20L dataset.}
\label{fig:uav20l}
\end{figure}

\begin{figure*}
\begin{center}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/FOC_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/OV_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/BC_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/POC_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/ARC_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/CM_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/FM_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/IV_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/LR_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/SOB_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/SV_overlap_OPE_AUC.png}
}
\subfigure[]{
	\includegraphics[width=0.234\linewidth]
	{images/UAV20L/VC_overlap_OPE_AUC.png}
}
\end{center}
   \caption{Success plots with attributes on UAV20L. Best viewed on color display.}
\label{fig:uav20l_attr}
\end{figure*}
\fi

>>>>

\begin{figure}[t]
    \includegraphics{Img/globally/Arch7.pdf}
    \caption{我们基于全球时空感知（GSTP）的跟踪系统的架构。}
    \label{fig:arch}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/globally/SiamRCNN.pdf}
    \caption{SiamRCNN 的网络结构示意图。}
    \label{fig:siamrcnn}
\end{figure*}

@@

\section{实验}
\label{sec:experiments}

\begin{figure}[htb]
    \includegraphics[width=1.0\textwidth]{Img/globally/success_plot.png}
    \caption{GOT-10k的总体性能，按其平均重叠（AO）得分进行排名。}
    \label{fig:ao}
\end{figure}

@@

\iffalse
\begin{figure}[t]
\begin{center}
\subfloat[]{
	\includegraphics[width=0.47\linewidth]
	{Img/globally/UAV20L/quality_plot_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.47\linewidth]
	{Img/globally/UAV20L/quality_plot_error_OPE_threshold.png}
}
\end{center}
   \caption{Success and precision plots on UAV20L dataset.}
\label{fig:uav20l}
\end{figure}
\fi

\begin{figure*}
\begin{center}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/FOC_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/OV_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/BC_overlap_OPE_AUC.png}
}\\
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/POC_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/ARC_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/CM_overlap_OPE_AUC.png}
}\\
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/FM_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/IV_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/LR_overlap_OPE_AUC.png}
}\\
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/SOB_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/SV_overlap_OPE_AUC.png}
}
\subfloat[]{
	\includegraphics[width=0.33\textwidth]
	{Img/globally/UAV20L/VC_overlap_OPE_AUC.png}
}
\end{center}
   \caption{Success plots with attributes on UAV20L. Best viewed on color display.}
\label{fig:uav20l_attr}
\end{figure*}
